---
title: "Homework 3"
author: "Key"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(ggridges)
library(ISLR)
```

1. Load the `{tidyverse}`, `{ggridges}`, and `{ISLR}` packages in the "setup" chunk. (Install any if needed.)

2. Run the following lines of code to read about and view the data we'll use for this lab.

- Comment out line 26 after you run it, but putting a `#` at the start of the line.

```{r gsscat, eval = FALSE}
str(gss_cat)
View(gss_cat)
?gss_cat
```

3. Use `{ggplot2}` to create a histogram of `tvhours`. The plot should:
  + Include a small amount of transparency so grid lines are visible under the histogram.
  + Be a different color than the default
  + Include meaningful axis labels
  + Have a title and a subtitle

```{r question-2}
theme_set(theme_minimal())

ggplot(gss_cat, aes(tvhours)) +
  geom_histogram(fill = "cornflowerblue", 
                 alpha = 0.7) +
  labs(x = "Number of Hours Watching Television",
       y = "Number of Observations",
       title = "Distribution of Television Watching",
       subtitle = "Data from the General Social Survey (http://gss.norc.org)")
```

4. Create a ridgeline density plot of `age` by `partyid`. Do you notice any strong  differences by party affiliation?

```{r question-3}
ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(fill = "cornflowerblue", alpha = 0.4)
```

5. Modify the plot from Question 4 to produce separate ridgeline densities by `race` within one plot. Do you see any patterns?

```{r question-4}
ggplot(gss_cat, aes(age, partyid)) +
  geom_density_ridges(aes(fill = race), alpha = 0.4)
```

6. Replicate the plots from Questions 4 and 5, but this time displaying the relations with boxplots (i.e., one boxplot from Question 4 and one boxplot for Question 5 in the chunk below). Try using `coord_flip`. Which do you think displays the relation more clearly? Why?
  
```{r label, options}
ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(fill = "cornflowerblue") +
  coord_flip()

ggplot(gss_cat, aes(partyid, age)) +
  geom_boxplot(aes(fill = race), alpha = 0.4) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

7. Run the following lines of code to get a correlation table as a data frame.

```{r corr-mat-df}

cor_tbl <- Hitters %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame() %>% 
  mutate(row = row.names(.)) %>% 
  gather(col, cor, -row) %>% 
  tbl_df()
```

Use the correlation table to create a heatmap using `geom_tile`. Change the colors to one of the four `viridis` palettes. What does the heatmap help you see?

```{r, heatmap}
ggplot(cor_tbl, aes(row, col, fill = cor)) +
  geom_tile() +
  scale_fill_viridis_c(option = "inferno") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

7. The code in the "barplot1" chunk below will produce a barplot. 

```{r barplot1}
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Use the code below to create a new data set - `gss_cat_new` - that redefines the `rincome` variable so that *Not applicable* is displayed first, followed by *No answer*, *Don't know*, *Refused*, and then each income category from lowest to highest. Once you've redefined the factor variable, re-produce the plot above by running the `ggplot` code at the bottom of the chunk. The plot should have *Not applicable* closest to the *y*-axis, then *No answer*, *Don't know*, etc.

```{r redfine-factor}
gss_cat_new <- gss_cat %>% 
  mutate(rincome = factor(rincome, levels = c("Not applicable",
                                              "No answer",
                                              "Don't know",
                                              "Refused",
                                              "Lt $1000",
                                              "$1000 to 2999",
                                              "$3000 to 3999",
                                              "$4000 to 4999",
                                              "$5000 to 5999",
                                              "$6000 to 6999",
                                              "$7000 to 7999",
                                              "$8000 to 9999",
                                              "$10000 - 14999",
                                              "$15000 - 19999",
                                              "$20000 - 24999",
                                              "$25000 or more")))
ggplot(gss_cat_new, aes(rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```